---
title: "k-means technical"
output: html_notebook
---

packages
```{r}
library(tidyverse)
library(cluster)
library(factoextra)
```

data
 100,000 residents for assault, murder, and rape in each of the 50 US states in 1973
```{r}
df <- USArrests
str(df)
```

remove any missing value
```{r}
df <- na.omit(df)
```

scaling/standardizing
```{r}
df <- scale(df)
head(df)
```

distance matrix from factoextra 
```{r}
distance <- get_dist (df)
fviz_dist(distance, gradient = list(low="#00AFBB", mid = "white", high = "#FC4E07"))
```

optimal number of clusters 
```{r}
library(NbClust)
df %>% 
NbClust(min.nc=2, max.nc=15, index="all", method="kmeans")
```





Computing k-means clustering in R
```{r}
k2 <- kmeans(df, centers = 4, nstart = 25)
str(k2)
```

```{r}
k2
```


rename those clusters according to their characteristics
```{r}
Kmean_Cluster<-factor(k2$cluster,levels = c(1,2,3,4),labels = c("Urban", "Rap", "NO!", "Murder"))
Kmean_Cluster
```



fviz_cluster for better illustration for 2 dim 
for more than two dim at first PCA then fviz_cluster
```{r}
fviz_cluster(k2, data = df)
```

pairwise scatter plots
CTRL + SHIFT + M
```{r}
  df %>% 
  as_tibble() %>%
  mutate(cluster = k2$cluster,
         state = row.names(USArrests)) %>%
  ggplot(aes(UrbanPop, Murder, color = factor(cluster), label = state)) + geom_text()
  
```


print final
```{r}
print(k2)
```

